\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Capital, \monthname{} \the\year{}
\makeatother}
\end{flushright}

My choice of engineering stemmed from a childish perspective I had as a child. I imagined engineering students are like scientists in science fiction movies.

But the reality of the two and a half years I spent in engineering college proved me that engineering (at least in Egypt) isn't much different from any other field.

I discovered that (just like in school) I'm studying to pass exams. It doesn't matter how well you understood the material; what matters is your ability to solve specific problems in a particular way. No creativity. No innovation. Nothing interesting.

This project might revive that childish perspective; it might prove that I wasn't 100\% wrong.

The past two years might have been preparation for what's to come, which might align with my old perception. who knows?

For the past two years, I've tried to force the education system to meet my expectations. But the system is bigger than me and everyone else. If it were that simple, everyone would do it.

Therefore, this is my last chance to try and live the experience I've looked for. If it doesn't work, I'll look for a field alongside engineering to fulfill my desire, and to be my way to earn money.

I hope my message, which I consider more important than the research, gets through.

I wrote this preface before starting the research, and I hope to achieve a result beyond my expectations.